---
title: "Dataset Cleaning"
author: "Bill Lang"
date: "3/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

```{r}
league <- read.csv("C:/Users/Billy/Desktop/Starcraft 2/Leauge.csv")
head(league)
```

```{r}
league <- league %>% 
  remove_rownames %>% 
  column_to_rownames(var="GameID")

league <- league %>% na.omit()
dim(league)
```

TotalHours and HoursPerWeek may be inproperly inputted (higher than is possible)

```{r}
league %>% group_by(HoursPerWeek) %>% summarise(number = n()) %>% arrange(desc(HoursPerWeek))
league %>% filter(HoursPerWeek > 56) %>% arrange(desc(HoursPerWeek))

#Any observations above 112 hours per week will be removed. This decision is arbitrary. 
#This is removing three observations. 

league <- league %>% filter(HoursPerWeek < 100) %>% arrange(desc(HoursPerWeek))
dim(league)
```

```{r}
league %>% group_by(TotalHours) %>% summarise(number = n()) %>% arrange(desc(TotalHours))
league %>% filter(TotalHours > 3000) %>% arrange(desc(TotalHours))

#Starcraft 2 had been out for over three years when this data was collected. The idea that a professional player would have half themax amount of hours (around 25,000/2) would be reasonable. Will be removing anyone with >9000 hours. THis is arbitrary. 

league <- league %>% filter(TotalHours < 9000) %>% arrange(desc(TotalHours))
dim(league)
```

These observations had been described as being repeated from idenitcal players and thus are being removed. 

```{r}

```








Another important thing to note is that many of the ingame actions are only signifigant in terms of the length of the game. With that in mind another dataset will be generated, dividing those important statistics by the max time stamp. Some statistics were collected per timestamp already (SelectByHotkeys, )

```{r}
leaguePerTimeStamp <- league
names(leaguePerTimeStamp)
df[,1:5] / df[,6] 
```



